\chapter*{Abstract}
\thispagestyle{empty}
As the Internet technology advances and number of connected nodes on the Internet
become very high, network security has turned out to be  one of the most important factors for organizations to consider.
Port scanning is one of the networking tools attackers use to understand the vulnerabilities in the network.
It is a robust technique used to discover the services running on a target machine.
While port scanners can be used for many research purposes, there is a high chance
of mistreating their high potential by attackers to enumerate the vulnerable ports in the
Internet. 
So, it is important to do a systematic study on how these scanners behave by analysing the incoming connection requests from them.\\\\
Aiming at Internet scanner's detection, we develop a network telescope to capture packets.
Network telescope is able to provide a sampled view of the Internet with regard to
illegitimate traffic.
It accomplishes this by monitoring ranges of unused internet address space where no active services or servers reside. 
Our objective is to check whether it is possible to identify the internet scanners and get meaningful data about behavior of these scanners using the small network telescope. 
Packet capturing take place during two different schedules.
We initially use passive network telescope to capture the packets.
Here ports are closed and rejecting any incoming connection requests.
Since network telescope consists of limited IP address space, we latter combine the initial system with honeypot to exploit the received connections by sending vulnerable replies.\\\\
This thesis focuses on the analysis, manipulation and visualisation of the packets captured from the two above mentioned setups and check if it is feasible to identify a pattern depending on the behavior of port scanners and transport layer protocols used to send the packets.
Moreover, it is also important to compare the obtained results of the initial configuration with the latter structure and check if the behavior has been changed.
Analysis was achieved by selecting correct suitable metrics that were used
to extract information from captured traffic. 
Through correct visualisation, we could infer the relevant information from obtained results of the analysis for further research. 

 